POPLMark goes Concurrent!\\Challenge problems for process calculi and behavioural types

### 2023-10-14 challenges/linearity.tex
updated proof of type safety

\begin{theorem}[Type safety]
  If \( \types{\Cempty}{P} \), then \( P \) is well formed.
\end{theorem}
\begin{proof}
  We proceed by induction on the definition of $\types{}{}$. The key
  cases are that for parallel composition and that for name
  restriction. In the case of parallel composition, linearity (and
  context splitting) ensure that every process in parallel will have
  different channel names. Then, the restriction rule enforces
  duality, therefore an output will be matched by an input.
\end{proof}

>>>>

\begin{theorem}[Type safety]
  If \( \types{\Cempty}{P} \), then \( P \) is well-formed.
\end{theorem}
\begin{proof}
  In order to prove that $P$ is well-formed, let us consider any
  process of the form
  $\Presd{x_1}{y_1}{\dots
    \Presd{x_n}{y_n}{(\Ppar{\Ppar{P_1}{P_2}}{R})}}$ that is
  structurally congruent to $P$. Moreover, assume that $P_1$ is
  prefixed at some $x_1$ and $P_2$ is prefixed at some $x_2$ such that
  $P_1\equiv\Pout{x}{v}{P_1'}$ (the opposite case proceeds
  similarly). We need to show that $P_2\equiv\Pin{x}{v}{P_2'}$. This
  can be easily done by contradiction. In fact, if
  $P_2\equiv\Pout{x}{v}{P_2'}$ then the typing rule for restriction
  would be violated since the type of $x_1$ and $y_1$ cannot be dual.
  % 
  % We proceed by induction on the definition of $\types{}{}$. The key
  % cases are that for parallel composition and that for name
  % restriction. In the case of parallel composition, linearity (and
  % context splitting) ensure that every process in parallel will have
  % different channel names. Then, the restriction rule enforces
  % duality, therefore an output will be matched by an input.
\end{proof}
